---
title: "A short demo of the anonymisation process"
author: "Sinan Shi"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    include: 
      in_header: vignettes/report.latex
---

```{r include=FALSE}
library(ccdata)
library(ccanonym)
library(pander)

panderOptions('table.split.table', 115)
```
```{r}
library(ccdata)
library(ccanonym)
```


# The YAML configuration file
Create a YAML configuration file as such, where the **identifiable variables**
(dirctVars), **key categorical variables** (keyVars), **key numerical
variables** (numVars), **key date-time variables** (datetimeVars), **sensitive variables**
(sensVars) and the corresponding operations and thresholds are specified. 
```{yaml}
directVars:
    - pasno		# PAS number
    - ICNNO		# Site code
    - ADNO		# INCNARC admission number 
    - NHSNO		# NHS number
    - TUADNO	# Transferrring unit admission number
    - DOB			# Date of birth 

keyVars:
    - GPCODE	# GP code
    - SEX			# Sex
    - PCODE 	# Postcode

sensVars:
    - BPC 		# Biopsy proven cirrhosis
    - AIDS_V3 # HIC/AIDS
    - PH 			# Portal hypertension
    - RAICU1	# Primary reason for admission to your unit
    - RAICU2 	# Secondary reasons for admission to your unit
    - URAICU 	# Ultimate primary reason for admission to unit

numVars:
    HCM: # Height
        microaggregation:
            aggr: 2

datetimeVars:
    DOAH:  # Date of original admission to/attendance at acute hospital'
        microaggregation: 
            aggr: 1
        addNoise: 
            noise: 2
    
    DAH: # Date of admission to your hospital
        addNoise: 
            noise: 2

    DOAICU:  # Date of original admission to ICU/HDU'
        microaggregation: 
            aggr: 1
        addNoise: 
            noise: 1
... ...

```
```{r}
conf <- yaml.load_file("../data/test_demo.yaml")
vars <- anony.var(conf)
```

# Identifiable data set


The identifiable data set is usually stored in ccRecord format. 
In the following code, we create  the ccRecord object from a XML file which
contains only five episodes.  
```{r load_packages, results="hide", warning=FALSE}
ccd <- xml2Data("../tests/data/test_data_anonym.xml")
demg.table <- as.data.frame(sql.demographic.table(ccd))

```
```{r pander}
all.var <- c(vars$dirv, vars$all.vars) # all variables besides non-confidential data 
pander(demg.table[, all.var],  style = 'rmarkdown')
```



# Anonymisation 

```{r, warning=FALSE}
anonccd <- anonymisation(ccd, conf="../data/test_demo.yaml")#, remove.alive=T, verbose=T)
pander(sql.demographic.table(anonccd)[, all.var, with=F], style="rmarkdown")
```
